HO unification from object language to meta language

### 2024-02-13 main.tex
update tex

\begin{equation}
  \texttt{\elpiIn{app[c "p", app[c "f", uv 0], lam x\ app[c "g", x, app[uv 1, x]]].}}
  \label{eq:elpi1}
\end{equation}

@@

\begin{equation}
  \texttt{\elpiIn{app[c "p", app[c "f", c "a"], lam x\ app[c "g", x, c "b"]].}}
\end{equation}

@@

In order to present the the compilation of the \ol terms so that higher order
unification can be performed, we need a second and mor powerful representation
of the \ol terms so that variables have a scope. This specification is shown
in the code snippet below.

@@

\begin{equation*}
  \texttt{\elpiIn{ml.lam x\ ml.lam y\ ml.uv 1 [x, y]}}
\end{equation*}

@@

\begin{equation*}
  \texttt{\elpiIn{ml.lam x\ ml.lam y\ ml.uv 0 [x]}}
\end{equation*}

@@

Moreover, if \elpiIn{ml.uv} stands for meta-variables, the \elpiIn{app} and the
\elpiIn{lam} constructors are the nodes for the terms of the \ol. Therefore, we
cannot claim that \elpiIn{ml.lam x\ ml.app [ml.c "f", x]} and \elpiIn{ml.c "f"}
unify, since, even though the first is the $\eta$-expansion of the second, the
\ml does not know how to $\eta\beta$-reduce the terms of the \ol.

@@

>>>>

\elpiInEq[eq:elpi1]{app[c "p", app[c "f", uv 0], lam x\ app[c "g", x, app[uv 1, x]]].}

@@

\begin{equation}
  \texttt{\elpiIn{app[c "p", app[c "f", c "a"], lam x\ app[c "g", x, c "b"]].}}
  \label{eq:elpi2}
\end{equation}

@@

In order to present the the compilation of the \ol terms, so that higher order
unification can be performed, we need a second and more powerful representation
of the \ol terms so that variables have a scope. This specification is shown
in the code snippet below.

@@

\elpiInEqq{ml.lam x\ ml.lam y\ ml.uv 1 [x, y]}

@@

\elpiInEqq{ml.lam x\ ml.lam y\ ml.uv 0 [x]}

@@

Moreover, if \elpiIn{ml.uv} stands for meta-variables, the \elpiIn{app} and the
\elpiIn{lam} constructors are the nodes for the terms of the \ol. Therefore, we
cannot claim that \elpiIn{ml.lam x\ ml.app [ml.c "f", x]} and \elpiIn{ml.c "f"}
unify, since, even though the first is the $\eta$-expansion of the second, the
\ml does not know how to $\eta\beta$-reduce terms of the \ol.

In our encoding, we explicitly encode the meta-variables with the \elpiIn{ml.uv}
constructor. This is because we prefer to have the full control of the \ml,
including the meta-variables instantiation. This way we are able to concretely
touch the substitution performed by the \ml. In a further section, we show that
there is no difference between our custom \ml language and any other \ml. Of
course, a full control on the unification behind meta-variable assignment ask to
drag the substitution mapping of the \ml and update it each time a variable is
refined.

@@

A link, \elpiIn{type link nat -> nat -> link}, takes two integers: the first 
stands for the index of variables in the \ol and the second is the index of 
the meta-variables.

For example, if we take back the example in \cref{eq:elpi2}, and want to compile
it, we obtain the new term:

\elpiInEq{app[c "p", app[c "f", c "a"], lam x\ app[c "g", x, c "b"]].}
